Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-03-09 introduction.tex

The numerical simulation of astronomical phenomena now plays a key role, along with observations and analytic theory, in pushing forward our understanding of the cosmos 
%\citep[e.g.,][]{DecadalSurvey01}.  
But we believe that with this role comes responsibility.  Those developing simulation tools must fulfill two key obligations: the first is to make those tools available to the community as a whole, much in the way that astronomical data is usually made publicly available.  The second is document, test and refinement those methods so that they can be critically evaluated and expanded by others.  This paper represents our attempt to meet our obligations with respect to the \enzo\ code.

>>>>

The numerical simulation of astronomical phenomena now plays a key role, along with observations and analytic theory, in pushing forward our understanding of the cosmos.
%\citep[e.g.,][]{DecadalSurvey01}.  
But we believe that with this role comes responsibility.  Those developing simulation tools must fulfill two key obligations: the first is to make those tools available to the community as a whole, much in the way that astronomical data is usually made publicly available.  The second is document, test and refineme those methods so that they can be critically evaluated and expanded by others.  This paper represents our attempt to meet our obligations with respect to the \enzo\ code.
